%-------------------------
% Resume in Latex
% Author : Bawi Thang
% Website: https://github.com/bawithahk/Resume.git
% License : UTA
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{www.github.com/bawithahk/}{\Large Bawi Thang}} & Email : \href{mailto:thangb44@gmail.com}{thangb44@gmail.com}\\
  \href{www.github.com/bawithahk/}{www.github.com/bawithahk} & Mobile : +1-214-486-9252 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Texas at Arlington}{Arlington, TX}
      {Bachelor of Science in Software Engineering;  GPA: 3.54}{Aug. 2018 -- May. 2022}
  \resumeSubHeadingListEnd

%--------Summary of Qualifications------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C/C++, Python, JavaScript, My-SQL, Java}}
   \item{     
     \textbf{Tools}{:  Notepad++, Visual Studio Code, PhpStorm, Sublime, NetBeans, Oracle VM VirtualBox, Ubuntu LTS,Git, GitHub, Git Bash, GitHub for Visual Studio and PhpStorm, gcc/g++, gdb}}
  \item{
     \textbf{Technologies}{: React, TextBlob, Praw, TensorFlow, Matplotlib, Pandas, NumPy, Scrum
     }
   \item{
     \textbf{Microsoft Office}{: Excel, Outlook, Word, PowerPoint}}
   \item{
     \textbf{OS}{: Windows, Mac OS, Unix, Linux}}
   
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Academic Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Natural Language Processing}
      {Successfully built an Android application with a team of 4 group members}
    \begin{itemize}
        \item Goal: to search and scan through Twitter API and create a data analysis table with Pie Chart to display the percentages of positivity, negativity, and neutrality of a string provided by the user.
        \item Utilized and applied React Native to build the UI framework and imported React, TextBlob, Praw libraries, and Twitter API to design the front-end and back-end of the application.
        \item Concluded the class and completed the project with a grade of ‘A’ and with great compliments on the project from the professor.
        \item GitHub Link: https://github.com/bawithahk/NaturalLanguageProcessing.git
    \end{itemize}
    \resumeSubItem{RollDice}
      {Developed a Poker-like game using a random generator representing dices. This C program rolls five dices randomly and display the Poker Hand Rankings of the outcomes.}
    \begin{itemize}
        \item GitHub Link: https://github.com/bawithahk/C-Projects.git 
    \end{itemize}
    \resumeSubItem{DrawTable}
      {Created a C program where a user can create a table with a specified size (1 -20) and fill it with a background character of choice. It, then, allows the user to draw on the table with drawing commands P, V, or H with a desired character of any kind. It also provides instructions on how to draw on the table during execution of the program.}
    \begin{itemize}
        \item GitHub Link: https://github.com/bawithahk/C-Projects.git 
    \end{itemize}
    \resumeSubItem{Academy Awards Guessing Game}
     {Constructed a classic Hangman-like C program/game where a user is allowed to guess the winner of Academy winners from a given category.}
    \begin{itemize}
        \item GitHub Link: https://github.com/bawithahk/C-Projects.git 
    \end{itemize}
  \resumeSubHeadingListEnd

%


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UTSI, UTA}{Arlington, TX}
      {Supplemental Instruction Leader}{Fall 2019 - Fall 2020}
      \resumeItemListStart
        \resumeItem{Lead Study Sessions}
          {Helped more than 60 percent of students in Calculus III class (Fall 2019, 2020) and C Programming class (Spring 2020) earn above B’s by leading study group sessions twice a week, holding review sessions at least twice before an exam, and providing extra resources like formula sheets for students.}
      \resumeItemListEnd

    \resumeSubheading
      {Echo-Link-Solutions}{Farmers Branch, TX}
      {Recruiter}{Summer 2018 - Summer 2019}
      \resumeItemListStart
        \resumeItem{Interviewed Candidates}
          {Posted multiple job openings on private social medias and company web page and led interviews with multiple candidates and reported the number of hired candidates weekly to company executives. Hired more than 30 candidates to work under the agency within a month of employment.}
        
      \resumeItemListEnd

   
  \resumeSubHeadingListEnd





%-------------------------------------------
\end{document}
